\documentclass[a4paper]{article}

\usepackage{amsthm, amsmath, latexsym, amssymb, verbatim}

\theoremstyle{definition} \newtheorem*{definition}{Definition}
\theoremstyle{definition} \newtheorem*{definitions}{Definitions}
\theoremstyle{plain} \newtheorem{theorem}{Theorem}[section]
\theoremstyle{plain} \newtheorem{proposition}[theorem]{Proposition}
\theoremstyle{plain} \newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{plain} \newtheorem{lemma}[theorem]{Lemma}
\theoremstyle{plain} \newtheorem{example}[theorem]{Example}

\begin{document}
\title{To Learn}
\author{Vatsal Kanoria}
\date{2022}
\maketitle
\begin{abstract}
This is the abstract
\end{abstract}
\tableofcontents


connections
(parallel transport)
((partition of unity))
curvature
(note that curvature form is generalisation of Riemann curvature tensor)

\section{Chern class of line bundle}
[Looks difficult in ref 2]
Look instead for ref for tautological line bundle on $\mathbb{C}P^1$

\section{Chern-Weil Homomorphism (Ref 1)}
Helpful in generalisation of the gauss bonet theorem.
(So understand gauss-bonet theorem as motivation?)

\begin{enumerate}
\item principle bundles on smooth manifolds
\item (why $n$-dim complex vector bundle is same as principle $GL_n(\mathbb{C})$ bundle over topological space.) (Why these are classified by homotopy classes of maps from $X$ to $B GL_n(\mathbb{C})$....and note that $B GL_n(\mathbb{C})$ is the infinite grassmanian $Gr_n(\mathbb{C}^\infty)$ of $n$-planes in $\mathbb{C}^\infty$.  (see reference 2) 
\item connection and curvature
\item de rham cohomology
\item complex (and real) lie group
\item Lie algebra of a lie group
\item ($\mathbb{C}[\mathfrak{g}]$ algebra of $\mathbb{C}$-valued polynomials on $\mathfrak{g}$
\item subalgebra of fixed points $\mathbb{C}[\mathfrak{g}]^G$ of $\mathbb{C}[\mathfrak{g}]$ under adjoint action of $G$. )
\item $H^*(M; \mathbb{C})$ for a principle bundle.  De Rham Cohomology.
\item How to obtain chern-weil homomorphism by taking invariant polys in the curvature of any connection on the given bundle. 
\begin{enumerate}
\item connection form
\item associated curvature form to connection form.  (i.e. if $\omega$ connection form,  then associated connection form is $D\omega$.  definition of exterior covarient derivative $D$. 
\item lie-algebra valued forms ??
\item closed forms
\end{enumerate}
\item Classifying Space
\end{enumerate}

\section{Chern classes}
This is an example/special case of chern-weil homomorphism,  with
$G=GL_n(\mathbb{C}$, $\mathfrak{g}=gl_n(\mathbb{C})$??
\begin{enumerate}
\item characteristic polynomial of $x\in \mathfrak{g}$ and invarient polys $f_k,  k=0, \ldots,  n$ given by the characteristic poly.
\item k-th chern class of smooth complex vector bundle $E$ as image of $f_k$ under Chern-Weil homomorphism of frame bundle of $E$
\item axioms of chern classes (see ref 1 and ref 2)
\item total chern class. (and show that it satisfies axioms of chern classes)

\section{Chern character}
This is an example/special case of chern-weil homomorphism

\end{enumerate}


\section{Characteristic classes of a principal bundle over a lie group}

Cohomology of classifying space of a lie group.  (its a certain algebra of invarient polys on the lie algebra)

Yoneda's lemma


\section*{References}
\begin{enumerate}
\item Wikipedia: Chern-Weil homomorphism
\item amathew.wordpress.com 
\end{enumerate}
\end{document}
